Statically Typed String Sanitation Inside a Python

### 2014-08-09 sanitation-psp14/sanitation-psp14-short.tex
Changed description of sanitation.
No longer motivates the fact that sanitation can be difficult, but this
paragraph should be in-line with our actual definition of sanitation found
later in the paper.

To avoid this problem, the program must \emph{sanitize} user input. For example, in this case, the developer (or, more often, a framework) might define a function \verb|sanitize| that prepends double quotes and existing backslashes  with a backslash, which SQL treats safely. Note that this function is not idempotent, so it should only be called once. Guaranteeing that user input has already been sanitized before it is used to construct a command is challenging.

@@

\section{Implementation in {Atlang}}
\begin{figure}
\begin{lstlisting}
@fn
def sanitize(s : string_in[r'.*']):
  return (s.replace(r'"', '&quot;') # TODO: is this right?
           .replace(r'<', '&lt;')
           .replace(r'>', '&gt;'))

>>>>

To avoid this problem, the program must \emph{sanitize} user input. 
For example, in this case, the developer (or, more often, a framework) might define a function \verb|sanitize| that escapes any double quotes, which are necessary in order to force uesr input to be interpreted as anything other than a string literal.
%prepends double quotes and existing backslashes  with a backslash, which SQL treats safely. Note that this function is not idempotent, so it should only be called once. Guaranteeing that user input has already been sanitized before it is used to construct a command is challenging.

@@

\section{Implementation in {Atlang}}
\begin{figure}
\begin{lstlisting}
#todo: why are these r's here?
#TODO-nrf this is maybe kind-of right bue I think there's a nicer way to do it.
@fn
def sanitize(s : string_in[r'.*']):
  return (s.replace(r'"', '&quot;') 
           .replace(r'<', '&lt;')
           .replace(r'>', '&gt;'))
